---
title: 'R INSTRUCTION: R COMMAND FOR SUMMARIZING DATAS'
author: "NGUYEN NGOC PHUNG"
date: "9/24/2020"
output: html_document
---

```{r}
#The following commands will generate plots of the data and summary statistics:
#1. Enter data into R:
x <- c(2, 6, 8, 12, 219, 30, 0, 25, 7, 16, 23, 38, 229, 35, 1, 228)
y <- c(9, 2, 24, 42, 9, 23, 23, 26, 5, 22, 214, 51, 65, 3, 216, 23)
```

### MEAN, MEDIAN
2. Mean: mean(x)
3. Median: median(x)

```{r}
mean(x)
median(x)
```

### HISTOGRAM, STEM AND LEAF, ORDERED DATA
4. Histogram: hist(x)
5. Stem-and-leaf plot: stem(x)
6. Ordered data: sort(x)
```{r}
#for example, I want bin=10, name of histogram is GOOD DAY
hist(x, breaks=23, main="GOOD DAY")
stem(x)
sort(x)
```

### PERCENTILE
 For example, calculate 60 percentile: quantile(x,0.6)
+ Another example: List 10, 20, · · · , 90, 100 percentile: quantile(x, seq(0, l, .l))
```{r}
quantile(x,0.6)
quantile(x,seq(0,1,0.1))
```

### QUARTILE
 Quantiles at, for example, p = .1, .34, .68, .93:
```{r}
p = c(.1, .34, .68, .93)
quantile (x, p)
```

### INTERQUARTILE RANGE
 Interquartile range: IQR(x)
```{r}
IQR(x)
```

### VARIANCE,STANDARD DEVIATION AND CORRELATION
 Variance: var(x)
```{r}
var(x)
```

 Standard deviation: sd(x)
```{r}
sd(x)
```

Correlation: cor(x, y)
```{r}
cor(x, y)
```

### BOXPLOT, SCATTERPLOT
12. Boxplot: boxplot(x)
```{r}
boxplot(x)
```

13. Scatterplot: plot(x, y)
```{r}
plot(x, y)
```

 
### LEAST SQUARE METHOD
```{r}
lm(x~y)
#I first plot x and y
plot(x,y)
#assign it to PHUNG
PHUNG<-lm(x~y)
#show regression line to plot
abline(PHUNG)
```

### THE END @-@
